Fast and scalable Gaussian process modeling of stellar variability \vspace{-3\baselineskip}

### 2016-12-19 paper/ms.tex
Minor edits

% Check to see that signs match
This power spectrum matches that of our basis kernel if $\omega_0^2 = c_j^2+d_j^2$,
$a_jc_j-b_jd_j = 0$, $b_jd_j+a_jc_j=\omega_0^2$, and $4c_j^2 = \omega_0^2/Q^2$.
The power spectrum can be normalized by $P_0$ in amplitude and $\omega_0$ in
frequency to yield a spectral shape that only depends upon $Q$.  This is plotted
in Figure \ref{sho_psd} for various values of $Q$.  This power spectrum has
a peak frequency given by $\omega_{max} = \omega_0\sqrt{1-1/(2Q^2)}$, which is
greater than zero for $Q > 1/\sqrt{2}$.

@@

The stochastically driven, damped simple-harmonic oscillator can then represent a wide range of intrinsic stellar variability, with
low $Q \approx 1$ representing granulation noise, and high $Q >> 1$ representing asteroseismic variability.

@@

\begin{enumerate}
\item AGN
\item RR Lyrae
\item Kepler with simulated transit
\item Asteroseismic target
\end{enumerate}

>>>>

% Check to see that signs match
This power spectrum matches that of our basis kernel if
\begin{eqnarray}
\omega_0^2 &=& c_j^2+d_j^2,\\
a_jc_j-b_jd_j &=& 0,\\
\omega_0^2&=& b_jd_j+a_jc_j ,\\
\omega_0^2/Q^2&=& 4c_j^2.
\end{eqnarray}
The power spectrum can be normalized by $P_0$ in amplitude and $\omega_0$ in
frequency to yield a spectral shape that only depends upon $Q$.  This is plotted
in Figure \ref{sho_psd} for various values of $Q$.  
Note that the oscillation frequency that appears in the kernel, $d_j$, differs
from that of the simple-harmonic oscillator, $\omega_0$, due to the damping
frequency, $c_j$.  This power spectrum has
a peak frequency given by $\omega_{max} = \omega_0\sqrt{1-1/(2Q^2)} = d_j$, which is
greater than zero for $Q > 1/\sqrt{2}$.

@@

The stochastically-driven, damped simple-harmonic oscillator can then represent a wide range of intrinsic 
stellar variability, with low $Q \approx 1$ representing granulation noise, and high $Q >> 1$ representing 
asteroseismic variability.

@@

\begin{enumerate}
\item AGN
\item RR Lyrae
\item Kepler with simulated transit
\item Asteroseismic target
\item Stellar rotational variability
\end{enumerate}
